Non-Vertical Cultural Transmission, Assortment, \\and the Evolution of Cooperation

### 2020-10-09 ms/main.tex
Add Fluctuations in spatial model figure

%%% Figure: Spatial model - global selection
\begin{figure}[h]
  \centering
   \includegraphics[scale=0.5]{{Ta=Tb_b=1.3_globalSelection}.pdf}
    ~
    \includegraphics[scale=0.5]{{Ta=0.4_Tb=0.3-0.5_b=1.3_globalSelection}.pdf} \\
  \caption{
  \textbf{Evolution of cooperation in a spatial model.}
  The expected frequency of cooperators in a structured population after 10,000 generations is shown (red for 0\%, green for 100\%) as function of both the cost of cooperation ($c$) on the y-axis, and the symmetric horizontal transmission rate ($T=T_A=T_B$) on the x-axis of the left panel, or the transmission bias $T_A-T_B$ on the x-axis of the right panel.
  The population evolves on a 100-by-100 grid.
  Cooperation and horizontal transmission are both local between adjacent sites, and each site had 8 neighbors.
  Selection operates globally (see \autoref{fig:spatial_local_selection} for results from a model with local selection).
  The black curves represent the cost boundaries for the evolution of cooperation in a well-mixed population with social association where $\alpha=1/8$ in (left) \autoref{eq:equal_transmission} and (right) \label{eq:cost_boundaries}.
  Simulations were stopped at generation 10,000 or if one of the phenotypes fixed and 50 simulations were executed for each parameter set.
  Here, population size is 10,000 (100-by-100 grid), benefit of cooperation, $b=1.3$, perfect vertical transmission $v=1$.
  \textbf{(left)} Symmetric horizontal transmission, $T=T_A=T_B$.
  \textbf{(right)} Horizontal transmission rates $T_A=0.4$, $0.3<T_B<0.5$.
  }
  \label{fig:spatial}
\end{figure}

%%% Figure: Spatial model - local selection
\begin{figure}[h]
  \centering
   \includegraphics[scale=0.5]{{Ta=Tb_b=1.3_localSelection}.pdf}
    ~
    \includegraphics[scale=0.5]{{Ta=0.4_Tb=0.3-0.5_b=1.3_localSelection}.pdf} \\
  \caption{
  \textbf{Evolution of cooperation in a spatial model and local selection.}
  The expected frequency of cooperators in a structured population after 10,000 generations is shown (red for 0\%, green for 100\%) as function of both the cost of cooperation ($c$) on the y-axis, and the symmetric horizontal transmission rate ($T=T_A=T_B$) on the x-axis of the left panel, or the transmission bias $T_A-T_B$ on the x-axis of the right panel.
  The population evolves on a 100-by-100 grid.
  Cooperation and horizontal transmission are both local between adjacent sites, and each site had 8 neighbors.
  Selection operates locally (see \autoref{fig:spatial} for results from a model with global selection).
  The black curves represent the cost boundaries for the evolution of cooperation in a well-mixed population with social association where $\alpha=1/8$ in (left) \autoref{eq:equal_transmission} and (right) \label{eq:cost_boundaries}.
  Simulations were stopped at generation 10,000 or if one of the phenotypes fixed and 50 simulations were executed for each parameter set.
  Here, population size is 10,000 (100-by-100 grid), benefit of cooperation, $b=1.3$, perfect vertical transmission $v=1$.
  \textbf{(left)} Symmetric horizontal transmission, $T=T_A=T_B$.
  \textbf{(right)} Horizontal transmission rates $T_A=0.4$, $0.3<T_B<0.5$.
  }
  \label{fig:spatial_local_selection}
\end{figure}

% TODO add figure of fluctuations in spatial model

>>>>

%%% Figure: Spatial model - global selection
\begin{figure}[h]
  \centering
   \includegraphics[scale=0.5]{{Ta=Tb_b=1.3_globalSelection}.pdf}
    ~
    \includegraphics[scale=0.5]{{Ta=0.4_Tb=0.3-0.5_b=1.3_globalSelection}.pdf} \\
  \caption{
  \textbf{Evolution of cooperation in a spatial model.}
  The expected frequency of cooperators in a structured population after 10,000 generations is shown (red for 0\%, green for 100\%) as function of both the cost of cooperation ($c$) on the y-axis, and the symmetric horizontal transmission rate ($T=T_A=T_B$) on the x-axis of the left panel, or the transmission bias $T_A-T_B$ on the x-axis of the right panel.
  The population evolves on a 100-by-100 grid.
  Cooperation and horizontal transmission are both local between adjacent sites, and each site had 8 neighbors.
  Selection operates globally (see \autoref{fig:spatial_local_selection} for results from a model with local selection).
  The black curves represent the cost boundaries for the evolution of cooperation in a well-mixed population with social association where $\alpha=1/8$ in ()\textbf{a}) \autoref{eq:equal_transmission} and \textbf{(b)} \autoref{eq:cost_boundaries}.
  Simulations were stopped at generation 10,000 or if one of the phenotypes fixed and 50 simulations were executed for each parameter set.
  Here, population size is 10,000 (100-by-100 grid), benefit of cooperation, $b=1.3$, perfect vertical transmission $v=1$.
  \textbf{(a)} Symmetric horizontal transmission, $T=T_A=T_B$.
  \textbf{(b)} Horizontal transmission rates $T_A=0.4$, $0.3<T_B<0.5$.
  }
  \label{fig:spatial}
\end{figure}

%%% Figure: Spatial model - local selection
\begin{figure}[h]
  \centering
   \includegraphics[scale=0.5]{{Ta=Tb_b=1.3_localSelection}.pdf}
    ~
    \includegraphics[scale=0.5]{{Ta=0.4_Tb=0.3-0.5_b=1.3_localSelection}.pdf} \\
  \caption{
  \textbf{Evolution of cooperation in a spatial model and local selection.}
  The expected frequency of cooperators in a structured population after 10,000 generations is shown (red for 0\%, green for 100\%) as function of both the cost of cooperation ($c$) on the y-axis, and the symmetric horizontal transmission rate ($T=T_A=T_B$) on the x-axis of the left panel, or the transmission bias $T_A-T_B$ on the x-axis of the right panel.
  The population evolves on a 100-by-100 grid.
  Cooperation and horizontal transmission are both local between adjacent sites, and each site had 8 neighbors.
  Selection operates locally (see \autoref{fig:spatial} for results from a model with global selection).
  The black curves represent the cost boundaries for the evolution of cooperation in a well-mixed population with social association where $\alpha=1/8$ in \textbf{(a)} \autoref{eq:equal_transmission} and \textbf{(b)} \autoref{eq:cost_boundaries}.
  Simulations were stopped at generation 10,000 or if one of the phenotypes fixed and 50 simulations were executed for each parameter set.
  Here, population size is 10,000 (100-by-100 grid), benefit of cooperation, $b=1.3$, perfect vertical transmission $v=1$.
  \textbf{(a)} Symmetric horizontal transmission, $T=T_A=T_B$.
  \textbf{(b)} Horizontal transmission rates $T_A=0.4$, $0.3<T_B<0.5$.
  }
  \label{fig:spatial_local_selection}
\end{figure}

% Fluctuations in spatial model
\begin{figure}[h]
  \centering
   \includegraphics[scale=0.75]{{timeSereis_b=1.3_TA=0.4_TB=0.435_c=0.02_globalSelection_normalizeByNumInteractions}.pdf}
   \caption{
    \textbf{Coexistence of both phenotypes in spatial model.}
    The dyanmics of the frequancy of cooperators (green) and the frequency of defactors in the spatial model. 
    Both groups has the same initial frequency (0.5) and there are no fixation of one of the groups through the simulation.
    The frequency of cooperators oscillate around the initial frequency. Here, population size is 10,000 (100-by-100 grid), benefit of cooperation, $b=1.3$, perfect vertical transmission $v=1$,
    horizontal transmission of cooperators $T_A = 0.4$, horizontal transmission of defactors $T_B = 0.435$ and cost $c=0.02$.
    }
    \label{fig:spatial_fluctuations}
  \end{figure}
  %TODO: edit this caption. DC
